Adaptive Shrinkage and False Discovery Rates by Laplace Approximation

### 2014-02-25 talks/UCstat2014.Rmd
updated and reran longer simulations after talk

- Buy a notebook; bring it to meetings; make notes! 
- Come to meetings with a written agenda. 
- While doing research, record what you did and what the outcome was.
- Use version control [git](http://git-scm.com) and internet repositories ([bitbucket](http://www.bitbucket.org), [github](http://www.github.com)) to organize notes, code, etc.
- Use knitr to help make your research reproducible.

@@

```{r, echo=FALSE,fig.height=3}
  plot(zdat[3,],zdat[4,],ylab="standard error",xlab="beta-hat")
  x[tail(order(zdat[3,])),]
```

@@

```{r, echo=FALSE}
x = read.table(paste0("../../stat45800/data/nobrega/expression/counts.txt"), header = TRUE)
xx = rowSums(x[,2:5])
x = x[xx>0,]
xx = xx[xx>0]
cbind(x[,1:5],pval,zdat.ash$lfdr)[c(15325,16123),]
```

>>>>

- Buy a notebook; bring it to meetings; make notes! 
- Come to meetings with a written agenda. 
- While doing research, record what you did and what the outcome was.
- Use version control ([git](http://git-scm.com)) and internet repositories ([bitbucket](http://www.bitbucket.org), [github](http://www.github.com)) to organize notes, code, etc.
- Use *knitr* to help make your research reproducible.

@@

```{r, echo=FALSE,fig.height=3}
  plot(zdat[3,],zdat[4,],ylab="standard error",xlab="beta-hat")
  dd[tail(order(zdat[3,])),]
```

@@

```{r, echo=FALSE}
dd = read.table(paste0("../../stat45800/data/nobrega/expression/counts.txt"), header = TRUE)
xx = rowSums(dd[,2:5])
dd = dd[xx>0,]
xx = xx[xx>0]
cbind(dd[,1:5],pval,zdat.ash$lfdr)[c(15325,16123),]
```
